A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-16 main.tex
Add comments for refs.

\begin{itemize}
   \item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}
   \item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
   \item MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
   \item Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
   \item A Logical Foundation for Environment Classifiers\cite{Tsukada}
   \item Environment classifiers\cite{taha2003environment}
   \item A framework for defining logics\cite{harper1993framework}
   \item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
   \item Refined Environment Classifiers\cite{kiselyov2016refined}
   \item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
   \item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
   \item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
   \item \red{Dependent types in practical programming}\cite{xi1999dependent}

        Section of Application
   \item \red{A dependently typed assembly language}\cite{xi2001dependently}
   \item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
   \item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
   \item \red{Run-time bytecode specialization}\cite{masuhara2001run}
   \item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
   \item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
   \item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}

>>>>

\begin{itemize}
   \item On Cross-Stage Persistence in Multi-Stage\cite{Hanada2014}

   CSPも入りました
   \item Eliminating Array Bound Checking Through Dependent Types\cite{Xi98}
   \item MetaML and Multi-stage Programming with Explicit Annotations\cite{MetaML}
   \item Idris, a general-purpose dependently typed programming language: Design and implementation\cite{brady2013idris}
   \item A Logical Foundation for Environment Classifiers\cite{Tsukada}
   \item Environment classifiers\cite{taha2003environment}
   \item A framework for defining logics\cite{harper1993framework}

    $\Sigma$ の使い方を確認した
   \item The Design and Implementation of {BER} MetaOCaml - System Description\cite{oleg2014}
   \item Refined Environment Classifiers\cite{kiselyov2016refined}
   \item Staging with control: type-safe multi-stage programming with control operators\cite{oishi2017staging}
   \item \red{Partial evaluation and automatic program generation}\cite{jones1993partial}
   \item \red{Efficient multi-level generating extensions for program specialization}\cite{gluck1995efficient}
   \item Dependent types in practical programming\cite{xi1999dependent}

        Section of Applicationを読んだ。Dead Code EliminationやLoop Unrollingにも使えるらしい。

   \item A dependently typed assembly language\cite{xi2001dependently}

   DTALの定義と制約solverを用いた型検査の定義
   \item \red{Run-time code generation and Modal-ML}\cite{wickline1998run}
   \item \red{C and tcc: a language and compiler for dynamic code generation}\cite{poletto1999c}
   \item \red{Run-time bytecode specialization}\cite{masuhara2001run}
   \item \red{A tour of Tempo: A program specializer for the C language}\cite{consel2004tour}
   \item \red{Optimizing ML with run-time code generation}\cite{lee1996optimizing}
   \item \red{Efficient incremental run-time specialization for free}\cite{marlet1999efficient}
